Mission-time LTL (MLTL) Formula Validation Via Regular Expressions\thanks{Work supported in part by [omitted for blind review] {\bf Note that all references to appendices will be replaced with URLs in the final paper; they are appendices only for blind review.}}

### 2022-10-12 paper/Paper.tex
small changes
fixed proof of correctness of WEST, added input / output to the 3 algorithms

\section{WEST Algorithm and Analysis} \label{WESTalg}
We now present the  full WEST algorithm, which takes MLTL formula $\phi$ (in NNF) and number of propositional variables $n$, and recursively computes all satisfying temporal regular expressions to $\phi$. 
We use C++ vectors of strings to represent alternation of regular expressions; for instance $\{t_1, t_2, ..., t_n\} = \bigcup_{i=1}^n t_i$. 
Additionally, we provide details for performing set intersection of temporal regular expressions, and the algorithm for the temporal operator $\mathcal{F}$. 
Note how the algorithm parallels the regular expression defined for $\mathcal{F}$, and the algorithms for the other three temporal operators follow an identical structure.

One major detail that drastically improves running time is applying a simplifying function to the output of set intersection. 
This is because the set intersection operation is repeatedly used to compute the temporal operators $\mathcal{G}, \mathcal{U}, \mathcal{R}$. 
Although set intersection does blow up exponentially in space in the worse case, it rarely does in practice; thus why we frequently simplify outputs. 
We simplify alternation by using the fact that for regular expressions $w_1$ and $w_2$, $w_1 1 w_2 \lor w_1 0 w_2 = w_1 s w_2$, and check for the reduction between at every index between every pair of strings in a given vector.

@@

% ZILI: Presenting algorithm vertically instead
\hspace{-5mm}
\begin{minipage}{0.52\textwidth}
\begin{algorithm}[H]
\caption{WEST Algorithm}
\begin{algorithmic}[1]
    \Procedure{reg}{string $\phi$, int $n$}
        \If{$\phi$ is $\top$ or $\bot$}
            \State return reg\_prop\_const($\phi$, n)
        \EndIf

@@

        \If{$\phi = \phi_1 \mathcal{R}_{[a, b]} \phi_2$}
            \State return reg\_R(reg($\phi_1$), reg($\phi_2$), a, b, n)
        \EndIf
    \EndProcedure
\end{algorithmic}
\end{algorithm}
\end{minipage}
\hfill
\begin{minipage}{0.48\textwidth}
\begin{algorithm}[H]
\caption{Takes set intersection of the languages of two regexes}
%Input: Vectors of strings that represent regexes, simplify boolean\\
%Output: Vector of strings that represents set intersection of the languages of the inputted regexes
\begin{algorithmic}
\Procedure{set\_intersect}{vector $R$, vector $T$, bool simp}
    \State Pad($R$, $T$), return $\leftarrow \{\}$
    \For{$(r, t) \in R\times T$}
            \State add bit\_wise\_and($r, t$) to ret 
    \EndFor
    \State return simplify(ret)
\EndProcedure
\end{algorithmic}
\end{algorithm}
\begin{algorithm}[H]
\caption{Computes the regex for a MLTL formula $\phi$U[a:b]$\psi$} 
%Inputs: Vectors of strings representing the regexes for $\phi$ and $\psi$, interval bounds, number of propositional variables, simplify boolean\\
%Output: Vector of strings that represents the appropriate satisfying computations 
\begin{algorithmic}
\Procedure{reg\_U}{vector reg\_phi, vector reg\_psi int $a$, int $b$, int $n$, bool simp} 
    \State comp $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{a} + $ reg\_psi
    \If{$a > b$} return $\{\}$
    \EndIf
    \For{($a \leq i \leq b-1$) }
        \State temp\_G1 $\leftarrow$ reg\_G(reg\_phi, $a$, $i$, $n$)
        \State \parbox[t]{.8\linewidth}{temp\_G2 $\leftarrow$ reg\_G(reg\_psi, $i+1$, \hspace*{5mm}$i+1$, $n$)}
        \State \parbox[t]{.8\linewidth}{temp\_comp $\leftarrow$ set\_intersect( \hspace*{5mm}temp\_G1, temp\_G2, $n$, simp)}
        \State \parbox[t]{.8\linewidth}{comp $\leftarrow$ join( comp, temp\_comp, \hspace*{5mm}simp)}
    \EndFor
    \State return comp
\EndProcedure
\end{algorithmic}
\end{algorithm}
\end{minipage}

\subsection{Theoretical Correctness of the WEST Algorithm}
 Correctness of the WEST algorithm is dependent on the correctness of subroutines \textit{reg\_prop\_cons}, \textit{reg\_prop\_var}, \textit{join}, \textit{set\_intersect}, \textit{reg\_F}, \textit{reg\_G}, \textit{reg\_U}, and \textit{reg\_R}. 
The routines \textit{reg\_prop\_cons} and \textit{reg\_prop\_var} takes as input a MLTL formula of the appropriate form, and returns the regular expression as previously defined in section \ref{regex}.
\textit{Join} takes as input two vectors of computation strings $R$ and $B$, and simply returns a vector containing all strings in $R$ and $B$, which is equivalent to $R \cup B$. 
\textit{Set\_intersect} takes as input two vectors of computation strings $R$ and $T$, where $R$ represents $r_1 | ... | r_a$ and $T$ represents $t_1 | ... | t_b$ such that each $r_i$ and $t_j$ are regular expressions over $\Sigma = \{`0', `1', `S', `,'\}$. Assume that all strings of regular expressions are right padded to equal length. We show that $\mathscr{L}(\textit{set\_intersect}(R, T)) = \mathscr{L}(R) \cap \mathscr{L}(T)$. Since a vector of regular expressions is synonymous to the collective Or of each of them, we have that 
    \mathscr{L}(R) \cap \mathscr{L}(T) &= \left(\bigcup_{i = 0}^a \mathscr{L}(r_i) \right)\cap \left( \bigcup_{j = 0}^b \mathscr{L}(t_j)\right) = \bigcup_{i = 0}^a \bigcup_{j = 0}^b \left(\mathscr{L}(r_i) \cap \mathscr{L}(t_j)\right).
\textit{Set\_intersect} computes the union of \textit{bit\_wise\_and}$(r_i, t_j)$ over all such pairs, and so it suffices to show $\mathscr{L}(\textit{bit\_wise\_and}(r_i, t_j)) = \mathscr{L}(r_i) \cap \mathscr{L}(t_j)$.  Given a computation $\pi$, $\pi \in \mathscr{L}(r_i) \cap \mathscr{L}(t_j)$ if and only if $\pi$ matches every character of both $r_i$ and $t_j$. $\textit{Bit\_wise\_and}(r_i, t_j)$ compares $r_i$ and $t_j$ character by character and computes their intersection, which is defined naturally: $0 \cap 1 = \emptyset,\ 0 \cap S = 0,\ 1 \cap S = 1, \ 0 \cap 0 = 0, \ 1 \cap 1= 1,\text{ and } S \cap S = S$. Note that this operation is commutative. This exhaustively captures all the cases for which $\pi$ must match corresponding characters from $r_i$ and $t_j$. Thus $\mathscr{L}(\textit{bit\_wise\_and}(r_i, t_j)) = \mathscr{L}(r_i) \cap \mathscr{L}(t_j)$ and the claim holds.
The correctness for \textit{reg\_F}, \textit{reg\_G}, \textit{reg\_U}, \textit{reg\_R}, and \textit{reg} will be proven by induction on depth of recursion to \textit{reg}. 
The depth of recursion is exactly the depth of the parse tree of the input formula.
For the base case (depth $0$), \textit{reg\_prop\_var} and \textit{reg\_prop\_cons} are called to handle input formulas that consist of a propositional variable, the negation of a propositional variable, or a propositional constant.
Then assume \textit{reg} is correct on all formulas of depth at most $d$, for some integer $d \geq 0$. Let $\gamma$ be a MLTL formula in negation normal form of depth $d + 1$. $\gamma$ must be of the form $\mathcal{G}_{[a,b]}\phi$, $\mathcal{F}_{[a,b]}\phi$, $\phi \mathcal{U}_{[a,b]} \psi$, or $\phi \mathcal{R}_{[a,b]} \psi$, such that $\phi$ and $\psi$ are of depth at most $d$, and $a$, $b$ are positive integers. The proof for all four cases are of similar structure, and it suffices to verify that the algorithms compute appropriate regular expressions correctly using \textit{join} and \textit{set\_intersect}.
We give the explicit proof for the case $\gamma = \phi \mathcal{U}_{[a,b]} \psi$ as an example.
In this case, \textit{reg} will call the helper function \textit{reg\_U} and pass in the parameters $\textit{reg\_phi} = \textit{reg}(\phi)$ and $\textit{reg\_psi} = \textit{reg}(\psi)$, which, by the induction hypothesis, are correctly and recursively computed. The regular expression for the Until operator may be rewritten as $\text{reg}(\phi \ \mathcal{U}_{[a,b]} \psi) = \text{reg}\left(\mathcal{G}_{[a, a]} \psi \right)\lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\phi \land \mathcal{G}_{[i+1, i+1]} \psi\right)$. In the pseudocode for $reg\_U$, the variable \textit{comp} is initialized to $(`1S"^n + ``,")^a$ pre-concatenated to \textit{reg\_psi}, and is the regular expression for $\mathcal{G}_[a, a] \psi$. Next, the Or block from $i = a + 1$ to $b - 1$ is iteratively computed using \textit{set\_intersect} for the inner expression, and added to \textit{comp} with the \textit{join} function, which are both proven correct above. This shows correctness of \textit{reg\_U}.
Continue in the same fashion to prove the other three cases, \textit{reg} is correct on all depth $d+1$ inputs, and thus \textit{reg} is correct on all inputs by induction.

@@

{\centering $\prod_{i = a}^b (n+1)i &= (n+1)^{b-a} \cdot \frac{b!}{(a-1)!} \leq (n+1)^\delta b! \leq (n+1)^\delta d!  = \mathcal{C}_G$ \\ $\sum_{i = a}^b (n+1)i &\leq (n+1)b\delta \leq (n+1)d\delta  = \mathcal{C}_F$\par}\\

@@

$\text{S(\emph{reg}}(\phi)) &= \sum_{i=a}^{b} (n+1)i \cdot \text{S(\emph{reg}}(\phi_{1})) < \mathcal{C}_{F} \text{S(\emph{reg}}(\phi_1)$.\\

@@

\begin{minipage}{.62\textwidth}
\begin{example} \label{example1}
Consider the MLTL formula:
$T \ \mathcal{U_{[\text{0,3}]}} p_0 = \mathcal{F_{[\text{0,3}]}}p_0$.
The WEST program outputs a union of regular expressions represented by the matrix in \eqref{matrix_ex3}. Instances like this demonstrate the utility of the regular expression simplification theorem; a recursive function implementation of this theorem would simplify output to the arbitrary computation. However, we foresee some challenges to the implementation of this algorithm.
\end{example}
\begin{minipage}{.38\textwidth}
%     \noindent \textbf{Example:}
    % \vspace{-0.05\textwidth}
\begin{equation} \label{matrix_ex3}
    1 & S & S & S\\
    S & 1 & S & S\\
    S & S & 1 & S\\
    S & S & S & 1\\
    0 & 0 & 0 & 0
\end{equation}

First, the proof of our algorithm relies on a set of $n+1$ regular expressions, yet it is obvious that the inclusion of redundant regular expressions of the same computation length in the union wouldn't alter this equivalence. A program implementation of this theorem would require an algorithm to parse through and identify which of these regular expressions are redundant and don't match the format of those described in our proof. For example, adding the row ``$1,1,1,1$" to the matrix generated by example \ref{example1} would change the matrix to not match the specifications of the theorem, but the union would still simplify to the arbitrary computation.
Next, it is possible that a regular expression could be appended with a substring of `$S$'s at the beginning or end. 
\begin{figure}[h!]
\begin{minipage}{.62\textwidth}
\begin{example} \label{example2}
Consider the following MLTL formula: $T \ \mathcal{U_{[\text{2,3}]}} p_0 \equiv \mathcal{F_{[\text{2,3}]}}p_0$. The WEST program generates a union of regular expressions corresponding to the matrix shown in \eqref{matrix_ex4}. It can clearly be seen that this is equivalent to the arbitrary computation, as one can remove the first two columns and apply the simplification theorem to the remaining columns.
\end{example}
\end{minipage}
\begin{minipage}{.38\textwidth}
\begin{equation} \label{matrix_ex4}
    \begin{pmatrix}
      S & S & 1 & S \\
      S & S & S & 1 \\
      S & S & 0 & 0
    \end{pmatrix}
\end{equation}
\end{minipage}
\end{figure}

@@

    \\\equiv  0\mathbf{S}\mathbf{S}1S0  \mathbf{S}\mathbf{S}1

>>>>

\section{WEST Algorithm and Analysis} \label{WESTalg}
We now present the  full WEST algorithm, which recursively computes all satisfying temporal regular expressions to a given MLTL formula (in NNF). 
We use C++ vectors of strings to represent alternation of regular expressions; for instance $\{t_1, t_2, ..., t_n\} = \bigcup_{i=1}^n t_i$. 
Additionally, we provide details for performing set intersection of temporal regular expressions, and the algorithm for the temporal operator $\mathcal{F}$. 
Note how the algorithm parallels the regular expression defined for $\mathcal{F}$, and the algorithms for the other three temporal operators follow an identical structure.

One major detail that drastically improves running time is applying a simplifying function to the output of set intersection. 
This is because the set intersection operation is repeatedly used to compute the temporal operators $\mathcal{G}, \mathcal{U}, \mathcal{R}$. 
Although repeated set intersection blows up exponentially in space in the worse case, it rarely does in practice; thus why we frequently simplify outputs. 
We simplify alternation by using the fact that for regular expressions $w_1$ and $w_2$, $\mathscr{L}(w_1 1 w_2 \lor w_1 0 w_2) = \mathscr{L}(w_1 s w_2)$, and check if the reduction applies at every index between every pair of strings in a given vector.

@@

% ZILI: Presenting algorithm vertically instead
\hspace{-5mm}
\begin{minipage}{0.52\textwidth}
\begin{algorithm}[H]
\caption{WEST Algorithm \\
Inputs: $\phi$ - MLTL formula in NNF \\
$\phi_1$ and $\phi_2$ below are subformulas of $\phi$\\
$n$ - number of propositional variables \\
Output: Vector of REGEX satsfying $\phi$}
\begin{algorithmic}[1]
    \Procedure{reg}{string $\phi$, int $n$}
        \If{$\phi$ is $\top$ or $\bot$}
            \State return reg\_prop\_const($\phi$, n)
        \EndIf

@@

        \If{$\phi = \phi_1 \mathcal{R}_{[a, b]} \phi_2$}
            \State return reg\_R(reg($\phi_1$), reg($\phi_2$), a, b, n)
        \EndIf
    \EndProcedure
\end{algorithmic}
\end{algorithm}
\vspace{5.9mm}
\end{minipage}
\hfill
\begin{minipage}{0.48\textwidth}
\begin{algorithm}[H]
\caption{set\_intersect}
Inputs: $R, T$ - Two Vectors of REGEX\\
$n$ - number of propositional variables\\
Output: Vector equal to $R \land T$
\begin{algorithmic}[1]
\Procedure{set\_intersect}{$R$, $T$, n}
    \State Pad($R$, $T$, n), return $\leftarrow \{\}$
    \For{$(r, t) \in R\times T$}
            \State add bit\_wise\_and($r, t$) to ret 
    \EndFor
    \State return simplify(ret)
\EndProcedure
\end{algorithmic}
\end{algorithm}
\vspace{-6.5mm}
\begin{algorithm}[H]
\caption{reg\_U} 
Inputs: r\_phi, r\_psi - vectors of REGEX for MLTL formulas $\phi$ and $\psi$ \\
$a, b$ - integers representing interval bound \\
$n$ - number of propositional variables\\
Output: Vector of REGEX for $\phi \mathcal{U}_{[a, b]} \psi$
\begin{algorithmic}[1]
\Procedure{reg\_U}{r\_phi, r\_psi, $a$, $b$, $n$} 
    \State comp $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{a} + $ r\_psi
    \If{$a > b$} return $\{\}$
    \EndIf
    \For{($a \leq i \leq b-1$) }
        \State temp\_G1 $\leftarrow$ reg\_G(r\_phi, $a$, $i$, $n$)
        \State \parbox[t]{.8\linewidth}{temp\_G2 $\leftarrow$ reg\_G(r\_psi, $i+1$, \hspace*{5mm}$i+1$, $n$)}
        \State \parbox[t]{.8\linewidth}{temp\_comp $\leftarrow$ set\_intersect( \hspace*{5mm}temp\_G1, temp\_G2, n)}
        \State \parbox[t]{.8\linewidth}{comp $\leftarrow$ join( comp, temp\_comp)}
        % , \hspace*{5mm}simp)}
    \EndFor
    \State return comp
\EndProcedure
\end{algorithmic}
\end{algorithm}
\end{minipage}

\subsection{Theoretical Correctness of the WEST Algorithm}
Correctness of the WEST algorithm is dependent on the correctness of subroutines \textit{reg\_prop\_cons}, \textit{reg\_prop\_var}, \textit{join}, \textit{set\_intersect}, \textit{reg\_F}, \textit{reg\_G}, \textit{reg\_U}, and \textit{reg\_R}. 
The routines \textit{reg\_prop\_cons} and \textit{reg\_prop\_var} takes as input a MLTL formula of the appropriate form, and returns the regular expression as previously defined in section \ref{regex}.
\textit{Join} concatenates two input vectors of computation strings $R$ and $T$, which is equivalent to $\mathscr{L}(R) \cup \mathscr{L}(T)$. 
\textit{Set\_intersect} takes as input two vectors of computation strings $R$ and $T$, where $R$ represents $r_1 | ... | r_a$ and $T$ represents $t_1 | ... | t_b$ such that each $r_i$ and $t_j$ are regular expressions over $\Sigma = \{`0', `1', `S', `,'\}$.
Assume that all strings of regular expressions are right padded to equal length. 
We show that $\mathscr{L}(\textit{set\_intersect}(R, T)) = \mathscr{L}(R) \cap \mathscr{L}(T)$. Since a vector of regular expressions is synonymous to the collective Or of each of them, we have that 
\begin{align*}
    \mathscr{L}(R) \cap \mathscr{L}(T) &= \left(\bigcup_{i = 0}^a \mathscr{L}(r_i) \right)\cap \left( \bigcup_{j = 0}^b \mathscr{L}(t_j)\right) = \bigcup_{i = 0}^a \bigcup_{j = 0}^b \left(\mathscr{L}(r_i) \cap \mathscr{L}(t_j)\right).
\end{align*}
The for loop in line 3 of \textit{set\_intersect} computes the union of \textit{bit\_wise\_and}$(r_i, t_j)$ over all such pairs, and so it suffices to show $\mathscr{L}(\textit{bit\_wise\_and}(r_i, t_j)) = \mathscr{L}(r_i) \cap \mathscr{L}(t_j)$.  
Given a computation $\pi$, $\pi \in \mathscr{L}(r_i) \cap \mathscr{L}(t_j)$ if and only if $\pi$ matches every character of both $r_i$ and $t_j$. 
$\textit{Bit\_wise\_and}(r_i, t_j)$ compares $r_i$ and $t_j$ character by character and computes their intersection, which is defined naturally: $0 \cap 1 = \emptyset,\ 0 \cap S = 0,\ 1 \cap S = 1, \ 0 \cap 0 = 0, \ 1 \cap 1= 1,\text{ and } S \cap S = S$. 
Note that this operation is commutative. This exhaustively captures all the cases for which $\pi$ must match corresponding characters from $r_i$ and $t_j$. 
Thus $\mathscr{L}(\textit{bit\_wise\_and}(r_i, t_j)) = \mathscr{L}(r_i) \cap \mathscr{L}(t_j)$ and the claim holds.

The correctness for \textit{reg\_F}, \textit{reg\_G}, \textit{reg\_U}, \textit{reg\_R}, and \textit{reg} will be proven by induction on depth of recursion to \textit{reg}. 
The depth of recursion is exactly the depth of the parse tree of the input formula.
For the base case (depth $0$), \textit{reg\_prop\_var} and \textit{reg\_prop\_cons} are called to handle input formulas that consist of a propositional variable, the negation of a propositional variable, or a propositional constant.
Then assume \textit{reg} is correct on all formulas of depth at most $d$, for some integer $d \geq 0$. 
Let $\gamma$ be a MLTL formula in negation normal form of depth $d + 1$. $\gamma$ must be of the form $\phi \lor \psi$, $\phi \land \psi$, $\mathcal{G}_{[a,b]}\phi$, $\mathcal{F}_{[a,b]}\phi$, $\phi \mathcal{U}_{[a,b]} \psi$, or $\phi \mathcal{R}_{[a,b]} \psi$, such that $\phi$ and $\psi$ are of depth at most $d$, and $a$, $b$ are positive integers. 
Correctness of the first two cases have been proven. 
The proof for the four temporal cases are of similar structure, and it suffices to verify that the algorithms compute appropriate regular expressions correctly using \textit{join} and \textit{set\_intersect}.

We give the explicit proof for the case $\gamma = \phi \mathcal{U}_{[a,b]} \psi$ as an example.
\textit{reg\_U} takes as input \textit{r\_phi} $=$ reg($\phi$) and \textit{r\_psi} $ = $ reg($\psi$), which by the induction hypothesis are correctly and recursively computed. 
The regular expression for the Until operator may be rewritten as $\text{reg}(\phi \ \mathcal{U}_{[a,b]} \psi) = \text{reg}\left(\mathcal{G}_{[a, a]} \psi \right)\lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\phi \land \mathcal{G}_{[i+1, i+1]} \psi\right)$. 
In line $2$ of \textit{reg\_U}, the variable \textit{comp} is initialized to $(`1S"^n + ``,")^a$ pre-concatenated to \textit{r\_psi}, and is the regular expression for $\mathcal{G}_[a, a] \psi$. 
Next, the $\lor$ from $i = a + 1$ to $b - 1$ is computed by the for loop in line 4; lines 5 through 7 computes $\text{reg}\left(\mathcal{G}_{[a,i]}\phi \land \mathcal{G}_{[i+1, i+1]} \psi\right)$. 
This shows correctness of \textit{reg\_U} (note that in a complete proof, correctness of \textit{reg\_G} needs to be shown first since lines 5 and 6 calls \textit{reg\_G}).
Continuing in the same fashion to prove the other three cases, \textit{reg} is correct on all depth $d+1$ inputs, and thus \textit{reg} is correct on all inputs by induction.

@@

{\centering $\prod_{i = a}^b (n+1)i = (n+1)^{b-a} \cdot \frac{b!}{(a-1)!} \leq (n+1)^\delta b! \leq (n+1)^\delta d!  = \mathcal{C}_G$ \\ $\sum_{i = a}^b (n+1)i \leq (n+1)b\delta \leq (n+1)d\delta  = \mathcal{C}_F$\par}

@@

$\text{S(\emph{reg}}(\phi)) = \sum_{i=a}^{b} (n+1)i \cdot \text{S(\emph{reg}}(\phi_{1})) < \mathcal{C}_{F} \text{S(\emph{reg}}(\phi_1)$.\\

@@

First, the proof of our algorithm relies on a set of $n+1$ regular expressions, yet it is obvious that the inclusion of redundant regular expressions of the same computation length in the union wouldn't alter this equivalence. A program implementation of this theorem would require an algorithm to parse through and identify which of these regular expressions are redundant and don't match the format of those described in our proof.

\begin{figure}[h!]
\begin{minipage}{.62\textwidth}
\begin{example} \label{example1}
Consider the MLTL formula:
$T \ \mathcal{U_{[\text{0,3}]}} p_0 = \mathcal{F_{[\text{0,3}]}}p_0$.
The WEST program outputs a union of regular expressions represented by the matrix in \eqref{matrix_ex3}. Instances like this demonstrate the utility of the regular expression simplification theorem; a recursive function implementation of this theorem would simplify output to the arbitrary computation. However, we foresee some challenges to the implementation of this algorithm.
\end{example}
\end{minipage}
\begin{minipage}{.38\textwidth}
%     \noindent \textbf{Example:}
    % \vspace{-0.05\textwidth}
\begin{equation} \label{matrix_ex3}
    \begin{pmatrix}
    1 & S & S & S\\
    S & 1 & S & S\\
    S & S & 1 & S\\
    S & S & S & 1\\
    0 & 0 & 0 & 0
    \end{pmatrix}
\end{equation}
\end{minipage}
\end{figure}

For example, adding the row ``$1,1,1,1$" to the matrix generated by example \ref{example1} would change the matrix to not match the specifications of the theorem, but the union would still simplify to the arbitrary computation. Next, it is possible that a regular expression could be appended with a substring of `$S$'s at the beginning or end.

\begin{figure}[h!]
\begin{minipage}{.62\textwidth}
\begin{example} \label{example2}
Consider the following MLTL formula: $T \ \mathcal{U_{[\text{2,3}]}} p_0 \equiv \mathcal{F_{[\text{2,3}]}}p_0$. The WEST program generates a union of regular expressions corresponding to the matrix shown in \eqref{matrix_ex4}. It can clearly be seen that this is equivalent to the arbitrary computation, as one can remove the first two columns and apply the simplification theorem to the remaining columns.
\end{example}
\end{minipage}
\begin{minipage}{.38\textwidth}
\begin{equation} \label{matrix_ex4}
    \begin{pmatrix}
      S & S & 1 & S \\
      S & S & S & 1 \\
      S & S & 0 & 0
    \end{pmatrix}
\end{equation}
\end{minipage}
\end{figure}

@@

    \equiv  0\mathbf{S}\mathbf{S}1S0  \mathbf{S}\mathbf{S}1
